Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-14 ms.qmd
Checked R2, I think we are explaining about 50%, which is good

```{r, global}
#| label: global
#| echo: false

@@

# How much variation does this model explain. Need to do this manually because function doesn't seme to work on the model object. We need to remember that predcit will include random effect variances so we may need to exclude this
  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x))

@@

# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
  r2 <- (v_fix - tot_re) / (v_fix)

  mean(r2) # Seems a bit high 
  quantile(r2, probs = c(0.025, 0.975))

>>>>

```{r, global}
#| label: global
#| echo: false
#| include: false

@@

# How much variation does this model explain. Need to do this manually because function doesn't seme to work on the model object. We need to remember that predcit will include random effect variances so we may need to exclude this
  re_post <- posterior_samples(model5_bayes, pars = "^sd_")
  v_fix <- apply(predict(model5_bayes, summary = FALSE), 1, function(x) var(x)) # 0.71 (but remember includes random effect variances)

# sigma2_v = typical sampling error variance**NEW STEP**
sub_data <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]
  sigma2_v <- sum(1 / sub_data$V) * (dim(sub_data)[1] - 1) /
              (sum(1 / sub_data$V)^2 - sum((1 / sub_data$V)^2))

# Now check that var fix from raw data and remove sampling variance. **NEW STEP**
  v_fix2 <- var(sub_data$effect_size) - sigma2_v  #0.58

@@

# Now, calculate r2 marginal, by subtracting the random effect variance from the fixed effect variance (which includes random effects). Need to check this as it may not be this intuitive
    r2 <- (v_fix - tot_re - sigma2_v) / (v_fix - sigma2_v) # Need to remove sampling variance too

    mean(r2) # Seems a bit high 0.5
  quantile(r2, probs = c(0.025, 0.975)); #0.27-0.69

# Now lets check with our different method. This should be close to the above. Which it is, so I think we're ok in our intuition.
  r2_2 <- (v_fix2 - tot_re) / (v_fix2) # Already removed sampling variance from v_fix2

  mean(r2_2) #  0.48
  quantile(r2_2, probs = c(0.025, 0.975)); #0.31-0.60
